A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-13 manuscript.Rmd
add overview table

>>>>

We have marked those steps that can be omitted as "optional" in the section headings.
Table \@ref(tab:overview) shows all steps required to to create and open and reproducible research project as they are presented in the remainder of the manuscript.

```{r overview, echo=FALSE}
overview <-
  read_csv(
    here::here("data", "overview.csv"),
    col_types = "cc",
    col_names = c("Phase", "Steps"),
    trim_ws = FALSE
  )
pander::pander(
  overview,
  split.tables = Inf,
  split.cells = Inf,
  missing = "",
  keep.line.breaks = TRUE,
  style = "grid",
  justify = 'left',
  caption = "Overview over all steps to create and open and reproducible research project."
)
```
